### 2021-09-15 papers.Rmd
first attempt

---
title: "papers"
site: distill::distill_article

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

aside_center <- function(text) {
  return(aside(center(list(text))))
}
```

## 2021

Lim, M. C., **Parsons, S.**, Goglio, A., Fox, E. (2021). Anxiety, stress, and binge eating behaviours in adolescence: a prospective approach. *Journal of Eating Disorders, 9*. [doi.org/10.1186/s40337-021-00444-2](https://doi.org/10.1186/s40337-021-00444-2)

**Parsons, S.**, (2021). splithalf: robust estimates of split half reliability. *Journal of Open Source Software, 6*(60), 3041, [doi.org/10.21105/joss.03041](https://doi.org/10.21105/joss.03041)

<div data-badge-type="donut" data-doi="10.21105/joss.03041" data-hide-no-mentions="true" class="altmetric-embed"></div>

<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>

**Parsons, S.**, Booth, C., Songco, A., & Fox, E. (2021). Emotional information-processing correlates of mental health in adolescence: A network analysis approach. *Cognition and Emotion* \\ [doi.org/10.1080/02699931.2021.1915752](https://doi.org/10.1080/02699931.2021.1915752). Preprint: [psyarxiv.com/8ygn](https://psyarxiv.com/8ygnh), data and code: [osf.io/mn5ek/](https://osf.io/mn5ek/)

Demkowicz, O., Panayiotou, M., **Parsons, S.**, Feltham, A., Arseneault, L., Ingram, B., Patalay, P., Edge D.,, Pierce, M., Creswell, C., Victor, C., O'Connor, R., & Qualter, P. (2021). Looking back to move forward: Reflections on the strengths and challenges of the COVID-19 UK mental health research response. 
*Frontiers Psychiatry*. [10.3389/fpsyt.2021.622562](https://doi.org/10.3389/fpsyt.2021.622562)

## 2020

Songco, A., Booth, C., Spiegler, O., **Parsons, S.**, & Fox, E. (2020). Anxiety and depressive symptom trajectories in adolescence and the co-occurring development of cognitive biases: Evidence from the CogBIAS longitudinal study. *Journal of Abnormal Child Psychology, 48*, 1617–1633, DOI: [10.1007/s10802-020-00694-9](https://doi.org/10.1007/s10802-020-00694-9)

Booth, C., Songco, A., **Parsons, S.**, & Fox, E. (2020). Cognitive mechanisms predicting resilient functioning in adolescence: Evidence from the CogBIAS longitudinal study. *Development and Psychopathology*, 1-9. DOI: [10.1017/S0954579420000668](https://doi.org/10.1017/S0954579420000668)

Dodd, H., Rayson, H., Ryan, Z., Bishop, C., **Parsons, S.**, Stuijfzand, B. (2020). Trajectories of anxiety when children start school: The role of behavioral inhibition and attention bias to angry and happy faces
*Journal of Abnormal Psychology*. DOI: [10.1037/abn0000623](https://doi.org/10.1037/abn0000623)

**Parsons, S.** (2020). Does attention bias modification induce structural brain changes? A commentary on Abend et al. (2019). *Biological Psychology, 152*. DOI: [10.1016/j.biopsycho.2020.107866](https://www.sciencedirect.com/science/article/pii/S0301051120300260). Preprint: [psyarxiv.com/4ze6h](https://psyarxiv.com/4ze6h/)

## 2019

Herbert, M., Notebaert, L., **Parsons, S.**, Fox, E., & MacLeod, C. (2019). The Effect of Varying Danger Controllability on Attention to Threat Messages. *Applied Cognitive Psychology, 34*(2). DOI: [10.1002/acp.3628](https://onlinelibrary.wiley.com/doi/abs/10.1002/acp.3628)[10.1002/acp.3628]

**Parsons, S.**, Kruijt, A-W., & Fox, E. (2019). Psychological Science needs a standard practice of reporting the reliability of cognitive behavioural measurements. *Advances in Methods and Practices in Psychological Science, 2,*(4), 378-395. DOI: [doi.org/10.1177/2515245919879695](https://doi.org/10.1177/2515245919879695). Preprint: [psyarxiv.com/6ka9z](https://psyarxiv.com/6ka9z)

Booth, C., Songco, A., **Parsons, S.**, Heathcote, L.C., & Fox, E. (2019). The CogBIAS longitudinal study of adolescence: Cohort profile and stability and change in measures across three waves. *BMC Psychology, 7*, 73. DOI: [10.1186/s40359-019-0342-8](https://bmcpsychology.biomedcentral.com/articles/10.1186/s40359-019-0342-8)

Crüwell, S., van Doorn, J., Etz, A., Makel, M.C., Moshontz, H., Niebaum, J., Orben, A., **Parsons, S.**, & Schulte-Mecklenbeck, M. (2019). 7 Easy Steps to Open Science: An annotated reading list. *Zeitschrift für Psychologie, 227*, 237-248. DOI: [doi.org/10.1027/2151-2604/a000387](https://doi.org/10.1027/2151-2604/a000387). Preprint: [psyarxiv.com/cfzyx](https://psyarxiv.com/cfzyx)

Kruijt, A-W., **Parsons, S.**, & Fox, E. (2019). A meta-analysis of bias at baseline in RCTs of attention bias modification: no evidence for bias towards threat in clinical anxiety and PTSD. *Journal of Abnormal Psychology, 128*(6), 563-573. DOI: 10.1037/abn0000406. Preprint DOI: [10.31234/osf.io/rfjup](10.31234/osf.io/rfjup)

## 2018

**Parsons, S.** (2018). Moving forward with questions of process and procedure in cognitive bias modification research: three points of consideration. *Published as an eLetter on* [10.1192/bjp.2018.43](https://doi.org/10.1192/bjp.2018.43). Preprint: [psyarxiv.com/k3vxc](https://psyarxiv.com/k3vxc)

Notebaert, L., Georgiades, J., Herbert, M., Grafton, B., **Parsons, S.**, Fox, E., & MacLeod, C. (2018). Trait anxiety and the alignment of attentional bias with controllability of danger. *Psychological Research*. DOI: [doi.org/10.1007/s00426-018-1081-9](https://doi.org/10.1007/s00426-018-1081-9)

## 2017

Lakens, et al. (2017). Justify Your Alpha: A Response to “Redefine Statistical Significance”. *Nature Human Behaviour, 2*, 168-171. DOI: [10.1038/s41562-018-0311-x](https://www.nature.com/articles/s41562-018-0311-x). Preprint: [psyarxiv.com/9s3y6/](https://psyarxiv.com/9s3y6/)

Booth, C., Songco, A., **Parsons, S.**, Heathcote, L., Vincent, J., Keers, R., & Fox, E. (2017). The CogBIAS longitudinal study protocol: cognitive and genetic factors influencing psychological functioning in adolescence. *BMC Psychology, 5*(1). DOI: [doi.org/10.1186/s40359-017-0210-3](https://doi.org/10.1186/s40359-017-0210-3)

## 2016

**Parsons, S**, Kruijt, A-W., & Fox, E. (2016). A cognitive model of psychological resilience. *Journal of Experimental Psychopathology, 7*(3), 296-310. DOI: http://dx.doi.org/10.5127/jep.053415

### 2021-09-24 index.Rmd
mini update papers

---
title: "Sam Parsons"
image: "SamProfile.jpg"
preview: "SamProfile.jpg"
twitter:
  site: "@sam_d_parsons"
links:
  - label: '<i class="fab fa-twitter"></i> Twitter'
    url: "https://twitter.com/sam_d_parsons"
  - label: '<i class="fab fa-github"></i> GitHub'
    url: "https://github.com/sdparsons"
  - label: '<i class="fas fa-envelope"></i> Email'
    url: "mailto:sam.parsons@psy.ox.ac.uk"
  - label: '<i class="ai ai-orcid"></i> ORCID'
    url: "https://orcid.org/0000-0002-7048-4093"
  - label: '<i class="ai ai-publons"></i> Publons'
    url: "https://publons.com/researcher/1351322/sam-parsons/"
  - label: '<i class="fab fa-youtube"></i> YouTube'
    url: "https://www.youtube.com/channel/UC3C_BRgKQNqZH2P2R5U2cfw"
  - label: '<i class="ai ai-osf"></i> OSF'
    url: "https://osf.io/k7akr/"
  - label: '<i class="ai ai-cv"></i> CV'
    url: "Sam_Parsons_cv.pdf"
output: 
  postcards::jolla
site: distill::distill_website
---

# [<i class="fab fa-twitter"></i>](https://twitter.com/sam_d_parsons) [<i class="ai ai-google-scholar"></i>](https://scholar.google.co.uk/citations?user=kE37Xy4AAAAJ&hl=en) [<i class="ai ai-orcid"></i>](https://orcid.org/0000-0002-7048-4093) [<i class="ai ai-osf"></i>](https://osf.io/k7akr/) [<i class="ai ai-researchgate"></i>](https://www.researchgate.net/profile/Sam_Parsons4) [<i class="fab fa-github"></i>](https://github.com/sdparsons) [<i class="ai ai-publons"></i>](https://publons.com/researcher/1351322/sam-parsons/) [<i class="fab fa-youtube"></i>](https://www.youtube.com/channel/UC3C_BRgKQNqZH2P2R5U2cfw) [<i class="fas fa-envelope-square"></i>](mailto:sam.parsons@psy.ox.ac.uk) [<i class="ai ai-cv"></i>](Sam_Parsons_cv.pdf)

# THIS IS A TEST SITE

## Researcher, Open Science Enthusiast, Lovable Bawbag

My name is Sam Parsons. I’m a Postdoctoral Research Associate in the Department of in Experimental Psychology at Oxford University. I work in the Oxford Centre for Emotion and Affective Neuroscience, aka OCEAN. Just in case you’re here for the cat, this ginger monster is called Beau.

As well as investigating cognitive-affective processes implicated in adolescent worry, I try to do my own small bit for the improvement of psychological science. Sometimes this is promoting open and reproducible research practices; others it is frustrating others by highlighting the importance of routinely estimating and reporting the reliability of our measurements. Mostly, I’d just like us all to get along and do good research.

I am happy to be contacted to discuss reliability of cognitive measures - particularly if you have questions about my splithalf package and need assistance with it.

(I try to keep this website up to date, however it may fall slightly behind. I do keep my CV up to date, so please do refer to that)

---------------------------

## splithalf

Estimate the internal consistency of your tasks with a permutation based split-half reliability approach.

Latest version: 0.8.1 “Rum Ham”

[<i class="fab fa-github"></i> Github documentation](https://github.com/sdparsons/splithalf)

Now published in the [Journal of Open Source Software](https://joss.theoj.org/papers/10.21105/joss.03041)

![splithalf package hexlogo](splithalf.png)

### 2021-09-29 _posts/2021-09-29-nomorehugo/nomorehugo.Rmd
adding functionality

---
title: "Bye Hugo Academic, hello Distill for Rmarkdown"
description: |
  Why I gave up on Hugo Academic
author:
  - name: Sam Parsons
    url: 
date: 09-29-2021
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

I grew to dislike Hugo Academic for building my website. To start this website, I thought I'd share some reflections on the transition to [Distill](https://rstudio.github.io/distill/).

## Why does Hugo hate me?

I loved it at first. Relatively easy to set up, nice formatting, works on Rmarkdown. Lots of positives.

Some months passed, and I needed to update papers. Nothing too problematic, but; copying a folder, entering all of the pieces of information, and finally completing new entries always took longer than I would like. Compared to my CV in overleaf, I can add new presentations and papers in 30 seconds, easy.

Added to this, every time there was a non-trivial update to any of R, blogdown, Hugo, something with netlify, or some combination of the way these things interact tended to break everything. Not to mention the transition to wowchemy. Every time this happened, the "easiest" thing to do was to rebuild the entire site.

Rebuilding the site was a) not fun, b) time consuming, and c) misses my main goal of having an easily update-able website. I want to make changes, build the site, and then push to github. I want to not enter rage every time.

I almost remade it again recently. I'm glad I searched for alternatives and, luckily, spotted a few nice website/blogs. They used distill

## Distill is less complicated

One of the first things I read was that there were fewer dependencies on other things, including, including themes, hugo, and netlify.

I still slightly prefer the Hugo Academic theme, but a simpler theme for less hassle is more than worth it. Personally, I'm liking that I can link my CV and not feel compelled to add every poster and presentation I have given to the website itself (not that you cant, but because it's not there by default you dont feel bad about not doing so)

## A few tips I came across or learned:

1. add the following to your theme.css file to use academic icons:
`@import url('https://cdn.rawgit.com/jpswalsh/academicons/master/css/academicons.min.css');`
You can then call the icons with something like the following (remember to replace the `fab` and `fa` with `ai`):
`<i class="ai ai-osf"></i>`

2. you can add a few themes with **postcards**, I kind of like not having too many options. You can do way more with css and html, but I want simplicity and efficiency in my life at the moment.

3. Adding altmertic badges is pretty easy, you can just add something like the following, copied from the [altmetric website](https://www.altmetric.com/products/altmetric-badges/)
<div data-badge-type="donut" data-doi="10.21105/joss.03041" data-hide-no-mentions="true" class="altmetric-embed"></div>

But, you'll likely also need to add the following so that it works ([from here](https://stackoverflow.com/questions/48883164/altmetric-badge-not-showing-in-rmarkdown-document/48905134))

<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>

### 2021-09-29 _posts/welcome/welcome.Rmd
adding functionality

---
title: "Welcome to My Blog"
description: |
  Welcome to our new blog, My Blog. We hope you enjoy 
  reading what we have to say!
author:
  - name: Nora Jones 
    url: https://example.com/norajones
    affiliation: Spacely Sprockets
    affiliation_url: https://example.com/spacelysprokets
date: 09-10-2021
output:
  distill::distill_article:
    self_contained: false
draft: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating blogs with Distill at:
# https://rstudio.github.io/distill/blog.html

```

### 2021-09-29 index.Rmd
adding functionality

@@
 
-# THIS IS A TEST SITE
+I’m a [Radboud Excellence Initiative](https://www.ru.nl/excellence/) Postdoctoral Research Fellow.
+I work in the [Lifespan Cognitive Dynamics Lab](https://www.rogierkievit.com/) based at the [Donders Institute](https://www.ru.nl/donders/).
+I did my DPhil in Experimental Psychology at the University of Oxford (a DPhil is a PhD but of course they need to call it something else)
 
-## Researcher, Open Science Enthusiast, Lovable Bawbag
-
-My name is Sam Parsons.
-I’m a Postdoctoral Research Associate in the Department of in Experimental Psychology at Oxford University.
-I work in the Oxford Centre for Emotion and Affective Neuroscience, aka OCEAN.
 Just in case you’re here for the cat, this ginger monster is called Beau.
 
-As well as investigating cognitive-affective processes implicated in adolescent worry, I try to do my own small bit for the improvement of psychological science.
+Radboud project
+
+Open Scholarship - ReproducibiliTea and FORRT
+
+I try to do my own small bit for the improvement of psychological science.
 Sometimes this is promoting open and reproducible research practices; others it is frustrating others by highlighting the importance of routinely estimating and reporting the reliability of our measurements.
@@
 
+Previous projects & talks
+
+Seriousness - not a huge fan
+
 I am happy to be contacted to discuss reliability of cognitive measures - particularly if you have questions about my splithalf package and need assistance with it.
 
-(I try to keep this website up to date, however it may fall slightly behind. I do keep my CV up to date, so please do refer to that)
+(I try to keep this website up to date, however it may fall slightly behind. I do keep my [CV](Sam_Parsons_cv.pdf) up to date, so please do refer to that)
 
@@
 
-![splithalf package hexlogo](splithalf.png)
+![](splithalf.png)

### 2021-09-29 papers.Rmd
mini update papers
adding functionality

@@
 
-aside_center <- function(text) {
-  return(aside(center(list(text))))
-}
 ```
@@
 Preprint: [psyarxiv.com/8ygn](https://psyarxiv.com/8ygnh), data and code: [osf.io/mn5ek/](https://osf.io/mn5ek/)
+
+<div data-badge-type="donut" data-doi="10.1080/02699931.2021.1915752" data-hide-no-mentions="true" class="altmetric-embed"></div>
+
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
 
@@
 Preprint: [psyarxiv.com/6ka9z](https://psyarxiv.com/6ka9z)
+
+<div data-badge-type="donut" data-doi="10.1177/2515245919879695" data-hide-no-mentions="true" class="altmetric-embed"></div>
+
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
 

### 2021-10-17 _posts/2021-09-29-nomorehugo/nomorehugo.Rmd
almost ready

@@
 
-I loved it at first. Relatively easy to set up, nice formatting, works on Rmarkdown. Lots of positives.
+I loved it at first.
+Relatively easy to set up, nice formatting, works on Rmarkdown.
+Lots of positives.
+The documentation to get started is also pretty nice, and plenty of researchers have written their own tutorials.
+
+But...
 
@@
 Nothing too problematic, but; copying a folder, entering all of the pieces of information, and finally completing new entries always took longer than I would like.
-Compared to my CV in overleaf, I can add new presentations and papers in 30 seconds, easy.
+Compare this to my CV in overleaf, I can add new presentations and papers in 30 seconds, easy.
 
-Added to this, every time there was a non-trivial update to any of R, blogdown, Hugo, something with netlify, or some combination of the way these things interact tended to break everything.
+Worse, every time there was a non-trivial update to any of R, blogdown, Hugo, something with netlify, or some combination of the way these things interact tended to break everything.
 Not to mention the transition to wowchemy.
 Every time this happened, the "easiest" thing to do was to rebuild the entire site.
+In for a 10 minute update, out for hours of frustrations.
 
@@
 
-One of the first things I read was that there were fewer dependencies on other things, including, including themes, hugo, and netlify.
+One of the first things I read was that there were fewer dependencies on other things, including, including themes, hugo, and netlify. I put together this fairly simple site, and I lije it so far.
 
@@
 3. Adding altmertic badges is pretty easy, you can just add something like the following, copied from the [altmetric website](https://www.altmetric.com/products/altmetric-badges/)
+`<div data-badge-type="donut" data-doi="10.21105/joss.03041" data-hide-no-mentions="true" class="altmetric-embed"></div>`
+
 <div data-badge-type="donut" data-doi="10.21105/joss.03041" data-hide-no-mentions="true" class="altmetric-embed"></div>
@@
 
-<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+`<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>`

### 2021-10-17 index.Rmd
almost ready

@@
 
-I’m a [Radboud Excellence Initiative](https://www.ru.nl/excellence/) Postdoctoral Research Fellow.
+**About me** I’m a [Radboud Excellence Initiative](https://www.ru.nl/excellence/) Postdoctoral Research Fellow.
 I work in the [Lifespan Cognitive Dynamics Lab](https://www.rogierkievit.com/) based at the [Donders Institute](https://www.ru.nl/donders/).
-I did my DPhil in Experimental Psychology at the University of Oxford (a DPhil is a PhD but of course they need to call it something else)
+I did my DPhil in Experimental Psychology at the University of Oxford^[a DPhil is a PhD but of course they need to call it something else]
 
@@
 
-Radboud project
+**My current work** is focused on the reliability of longitudinal structural brain imaging data across brain regions, structural measures, and studies.
+My aim is to support developmental cognitive neuroscience study changes in brain structure and function by focusing on sources of reliability and error.
+My core approach will be based on intra-class effect decomposition, closely tied to generalisability theory.
+These models extract sources of variation in order to explore where the variation/error comes from in the model, moving beyond a single metric of reliability (e.g.
+ICC for test-retest).
+I believe it is important to support others who may want to use these approaches, so I will be dedicating time to share code and develop tutorials.
 
-Open Scholarship - ReproducibiliTea and FORRT
+I am happy to be contacted to discuss reliability of cognitive measures - particularly if you have questions about my splithalf package (see below) and need assistance with it.
 
-I try to do my own small bit for the improvement of psychological science.
-Sometimes this is promoting open and reproducible research practices; others it is frustrating others by highlighting the importance of routinely estimating and reporting the reliability of our measurements.
-Mostly, I’d just like us all to get along and do good research.
+**Open Scholarship** I try to do my own small bit for the improvement of psychological science and open scholarship.
+Amy Orben, Sophia Cruwell, and I co-founded the [ReproducibiliTea Journal Clubs](https://reproducibilitea.org/) - now a large international community of Journal Clubs where folks talk about openness, reproducibility, and improving research practices.
+Flavio Azevedo and I also co-founded a [Framework for Open and Reproducible Research Training](https://forrt.org/) (FORRT), a pedagogy-focused community working to support those seeking to incorporate open and reproducible practices into their teaching and mentoring.
 
-Previous projects & talks
-
-Seriousness - not a huge fan
-
-I am happy to be contacted to discuss reliability of cognitive measures - particularly if you have questions about my splithalf package and need assistance with it.
-
-(I try to keep this website up to date, however it may fall slightly behind. I do keep my [CV](Sam_Parsons_cv.pdf) up to date, so please do refer to that)
+Eventually, I will get around to loading my previous projects & talks here.
+In the meantime, I have most of my talk slides on the [OSF](https://osf.io/rfy2h/), and you can check out my [CV](Sam_Parsons_cv.pdf).
+I do try to keep this website up to date, however it may fall behind my CV.
 
@@
 
-Latest version: 0.8.1 “Rum Ham”
+Latest version: 0.8.1 “Rum Ham”^[Yes, all of the version names I have given the package are references to It's Always Sunny in Philadelphia.
+The pointlessness amuses me, and academia is often too serious, so count this as a minor act of rebellion]
 
@@
 
-![](splithalf.png)
+![](splithalf.png){ width=50% }

### 2021-10-17 papers.Rmd
almost ready

--- 2021-09-15 papers.Rmd
@@
 ---
-title: "papers"
-site: distill::distill_article
-
+title: "publications"
+output:
+  distill::distill_article:
+    toc: true
+    toc_depth: 3
+    toc_float: true
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
-
-aside_center <- function(text) {
-  return(aside(center(list(text))))
-}
 ```
 
-## 2021
+## Peer-reviewed
+
+### 2021
 
@@
 
+<aside>
+<div data-badge-type="donut" data-doi="10.1186/s40337-021-00444-2" data-hide-no-mentions="true" class="altmetric-embed"></div>
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
+
 **Parsons, S.**, (2021). splithalf: robust estimates of split half reliability. *Journal of Open Source Software, 6*(60), 3041, [doi.org/10.21105/joss.03041](https://doi.org/10.21105/joss.03041)
 
+<aside>
 <div data-badge-type="donut" data-doi="10.21105/joss.03041" data-hide-no-mentions="true" class="altmetric-embed"></div>
-
 <script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
 
@@
 
+<aside>
+<div data-badge-type="donut" data-doi="10.1080/02699931.2021.1915752" data-hide-no-mentions="true" class="altmetric-embed"></div>
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
+
 Demkowicz, O., Panayiotou, M., **Parsons, S.**, Feltham, A., Arseneault, L., Ingram, B., Patalay, P., Edge D.,, Pierce, M., Creswell, C., Victor, C., O'Connor, R., & Qualter, P.
@@
 
-## 2020
+<aside>
+<div data-badge-type="donut" data-doi="10.3389/fpsyt.2021.622562" data-hide-no-mentions="true" class="altmetric-embed"></div>
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
+
+### 2020
 
@@
 *Journal of Abnormal Child Psychology, 48*, 1617–1633, DOI: [10.1007/s10802-020-00694-9](https://doi.org/10.1007/s10802-020-00694-9)
+
+<aside>
+<div data-badge-type="donut" data-doi="10.1007/s10802-020-00694-9" data-hide-no-mentions="true" class="altmetric-embed"></div>
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
 
@@
 
+<aside>
+<div data-badge-type="donut" data-doi="10.1017/S0954579420000668" data-hide-no-mentions="true" class="altmetric-embed"></div>
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
+
 Dodd, H., Rayson, H., Ryan, Z., Bishop, C., **Parsons, S.**, Stuijfzand, B.
@@
 *Journal of Abnormal Psychology*. DOI: [10.1037/abn0000623](https://doi.org/10.1037/abn0000623)
+
+<aside>
+<div data-badge-type="donut" data-doi="10.1037/abn0000623" data-hide-no-mentions="true" class="altmetric-embed"></div>
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
 
@@
 
-## 2019
+<aside>
+<div data-badge-type="donut" data-doi="10.1016/j.biopsycho.2020.107866" data-hide-no-mentions="true" class="altmetric-embed"></div>
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
+
+### 2019
 
@@
 DOI: [10.1002/acp.3628](https://onlinelibrary.wiley.com/doi/abs/10.1002/acp.3628)[10.1002/acp.3628]
+
+<aside>
+<div data-badge-type="donut" data-doi="10.1002/acp.3628" data-hide-no-mentions="true" class="altmetric-embed"></div>
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
 
@@
 
+<aside>
+<div data-badge-type="donut" data-doi="10.1177/2515245919879695" data-hide-no-mentions="true" class="altmetric-embed"></div>
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
+
 Booth, C., Songco, A., **Parsons, S.**, Heathcote, L.C., & Fox, E.
@@
 DOI: [10.1186/s40359-019-0342-8](https://bmcpsychology.biomedcentral.com/articles/10.1186/s40359-019-0342-8)
+
+<aside>
+<div data-badge-type="donut" data-doi="10.1186/s40359-019-0342-8" data-hide-no-mentions="true" class="altmetric-embed"></div>
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
 
@@
 
+<aside>
+<div data-badge-type="donut" data-doi="10.1027/2151-2604/a000387" data-hide-no-mentions="true" class="altmetric-embed"></div>
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
+
 Kruijt, A-W., **Parsons, S.**, & Fox, E.
@@
 
-## 2018
+<aside>
+<div data-badge-type="donut" data-doi="10.1037/abn0000406" data-hide-no-mentions="true" class="altmetric-embed"></div>
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
+
+### 2018
 
@@
 Preprint: [psyarxiv.com/k3vxc](https://psyarxiv.com/k3vxc)
+
+<aside>
+<div data-badge-type="donut" data-doi="10.1192/bjp.2018.43" data-hide-no-mentions="true" class="altmetric-embed"></div>
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
 
@@
 
-## 2017
+<aside>
+<div data-badge-type="donut" data-doi="10.1007/s00426-018-1081-9" data-hide-no-mentions="true" class="altmetric-embed"></div>
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
+
+### 2017
 
@@
 
+<aside>
+<div data-badge-type="donut" data-doi="10.1038/s41562-018-0311-x" data-hide-no-mentions="true" class="altmetric-embed"></div>
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
+
 Booth, C., Songco, A., **Parsons, S.**, Heathcote, L., Vincent, J., Keers, R., & Fox, E.
@@
 
-## 2016
+<aside>
+<div data-badge-type="donut" data-doi="10.1186/s40359-017-0210-3" data-hide-no-mentions="true" class="altmetric-embed"></div>
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
+
+### 2016
 
 **Parsons, S**, Kruijt, A-W., & Fox, E. (2016). A cognitive model of psychological resilience. *Journal of Experimental Psychopathology, 7*(3), 296-310. DOI: http://dx.doi.org/10.5127/jep.053415
+
+<aside>
+<div data-badge-type="donut" data-doi="10.5127/jep.053415" data-hide-no-mentions="true" class="altmetric-embed"></div>
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
+
+## Preprints and working papers
+
+**Parsons, S** (2020).
+Exploring reliability heterogeneity with multiverse analyses: Data processing decisions unpredictably influence measurement reliability.
+Under review at Meta-Psychology.
+Preprint: [psyarxiv.com/y6tcz](https:/psyarxiv.com/y6tcz), data and code: [osf.io/haz6u/](https://osf.io/haz6u/)
+
+FORRT. (2019). Introducing a Framework for Open and Reproducible Research Training (FORRT). (Co-author). Preprint: [osf.io/bnh7p/](https://osf.io/bnh7p/). Website: [forrt.org](https://forrt.org)
+
+**Parsons, S** (2019). Visualising two approaches to explore reliability-power relationships. Preprint: [psyarxiv.com/qh5mf](https://psyarxiv.com/qh5mf)

### 2021-11-15 index.Rmd
email update

@@
   - label: '<i class="fas fa-envelope"></i> Email'
-    url: "mailto:sam.parsons@psy.ox.ac.uk"
+    url: "mailto:sam.parsons@radboudumc.nl"
   - label: '<i class="ai ai-orcid"></i> ORCID'
@@
 
-# [<i class="fab fa-twitter"></i>](https://twitter.com/sam_d_parsons) [<i class="ai ai-google-scholar"></i>](https://scholar.google.co.uk/citations?user=kE37Xy4AAAAJ&hl=en) [<i class="ai ai-orcid"></i>](https://orcid.org/0000-0002-7048-4093) [<i class="ai ai-osf"></i>](https://osf.io/k7akr/) [<i class="ai ai-researchgate"></i>](https://www.researchgate.net/profile/Sam_Parsons4) [<i class="fab fa-github"></i>](https://github.com/sdparsons) [<i class="ai ai-publons"></i>](https://publons.com/researcher/1351322/sam-parsons/) [<i class="fab fa-youtube"></i>](https://www.youtube.com/channel/UC3C_BRgKQNqZH2P2R5U2cfw) [<i class="fas fa-envelope-square"></i>](mailto:sam.parsons@psy.ox.ac.uk) [<i class="ai ai-cv"></i>](Sam_Parsons_cv.pdf)
+# [<i class="fab fa-twitter"></i>](https://twitter.com/sam_d_parsons) [<i class="ai ai-google-scholar"></i>](https://scholar.google.co.uk/citations?user=kE37Xy4AAAAJ&hl=en) [<i class="ai ai-orcid"></i>](https://orcid.org/0000-0002-7048-4093) [<i class="ai ai-osf"></i>](https://osf.io/k7akr/) [<i class="ai ai-researchgate"></i>](https://www.researchgate.net/profile/Sam_Parsons4) [<i class="fab fa-github"></i>](https://github.com/sdparsons) [<i class="ai ai-publons"></i>](https://publons.com/researcher/1351322/sam-parsons/) [<i class="fab fa-youtube"></i>](https://www.youtube.com/channel/UC3C_BRgKQNqZH2P2R5U2cfw) [<i class="fas fa-envelope-square"></i>](mailto:sam.parsons@radboudumc.nl) [<i class="ai ai-cv"></i>](Sam_Parsons_cv.pdf)
 

### 2022-01-30 _posts/2021-09-29-nomorehugo/nomorehugo.Rmd
publish acronyms post

@@
   Why I gave up on Hugo Academic
-author:
-  - name: Sam Parsons
-    url: 
 date: 09-29-2021

### 2022-01-30 _posts/2022-01-29-acronyms/acronyms.Rmd
publish acronyms post

---
title: "Many Papers (MP) have Too Many Acronyms (TMA)"
description: |
  Scientific articles contain way too many acronyms.
date: 01-29-2022
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Some acronyms are used so widely used that spelling them out is not needed. For example, ECR for Early Career Researcher. Or more field specific, such as RT for Response Time, or GWAS for Gene-Wide Association Study. Acronyms do run into trouble when they could indicate different concepts: e.g. does your ML mean Multi-Level? Machine Learning? Maximum Likelihood?

More often than not, using Too Many Acronyms (TMA) can make your writing harder to read.^[Yes, sometimes acronyms are well used. And No, this is not at attempt to lash out at those that find them useful. It is an account of why relying on them can make things more challenging for the reader]

A pithy example:

Many writers use Too Many Acronyms (TMA). Two challenging sub types of TMA are Too Many Unusual (unfamiliar works too) Acronyms (TMUA) and Too Many Overlapping Acronyms (TMOA; Similar also works, but then we would use TMSA). When TMA (or TMUA) occurs, the writing is both Hard To Read (HTR) and Hard To Follow (HTF). Writing that is HTR makes individual sentences more difficult to parse, insofar as it requires the reader to employ more executive control (EC) and Working Memory (WM) to recall TMA in order to understand the sentence. A knock on effect is that the writing becomes HTF, i.e. the reader must continually check All the Acronyms (AtA1) and All the Abbreviations (AtA2) to ensure they are following the thread of the argument. If the reader is anything like me, eventually the acronym becomes separate to whatever it refers. Then the reader is reading many instances of FCT2A as just a string of characters that is somehow important. Reducing TMA (and especially TMUA and TMOA/TMSA) should help avoid both HTR and HTR writing, leaving readers with EC/WM solely for your arguments.

# Why acronyms?

Internet ramblings aside, I do see acronyms being overused. One of my regular comments as a peer reviewer is to remove at least one acronym from the text. No, not to be pedantic or because I have my favourite reviewer 2 comments. I truly find papers that use an excessive amount of acronyms harder to read and harder to follow. I see three broad reasons for using excessive acronyms:

1. To reduce the word count. Consider how many words you are saving, is that worth the additional challenge readers have? I've seen an acronyms used that would barely affect the word count. I bet there are filler words that could be removed instead. 
2. To try to make things easier to read by not repeating the same key phrase many, many times. This is one of the times I can get behind a paper-specific acronym. But, consider asking someone to read the same few paragraphs with and without the acronyms, I'd wager that the paragraphs without are easier to read and understand. 
3. To signify that the term is key to the paper. By ensuring the reader has to spend extra energy remembering the acronym, you try to get them to keep this key concept in mind. Great, until you're 5 acronyms deep and in 2 paragraphs the reader has forgotten most of them.

Of course, I'm just an Early Career Researcher^[ECR, if you will.] rambling on my own website. So, of course these thoughts are not prescriptive, nor do I think they apply across all contexts. In the end, the readers are the judges. So, lets be as kind to them as possible.

### 2022-02-24 index.Rmd
check github
update photo

@@
 title: "Sam Parsons"
-image: "SamProfile.jpg"
-preview: "SamProfile.jpg"
+image: "SP_Profile.jpg"
+preview: "SP_Profile.jpg"
 twitter:
@@
 
-**About me** I’m a [Radboud Excellence Initiative](https://www.ru.nl/excellence/) Postdoctoral Research Fellow.
+**About me** I am a [Radboud Excellence Initiative](https://www.ru.nl/excellence/) Postdoctoral Research Fellow.
 I work in the [Lifespan Cognitive Dynamics Lab](https://www.rogierkievit.com/) based at the [Donders Institute](https://www.ru.nl/donders/).
 I did my DPhil in Experimental Psychology at the University of Oxford^[a DPhil is a PhD but of course they need to call it something else]
-
-Just in case you’re here for the cat, this ginger monster is called Beau.
 

### 2022-02-24 papers.Rmd
update photo

@@
 
+(please note: I will add pdfs links asap)
+
 ## Peer-reviewed
+
+### 2022
+
+Azevedo, F., Lui, M., Pennington, C., Pownall, M., Evans, T., **Parsons, S.**, Elsherif, M., Micheli, L., Westwood, S., & Framework for Open and Reproducible Research Training (FORRT).
+(2022).
+Towards a culture of open scholarship: the role of pedagogical communities.
+*BMC Research Notes, 15*, 75.
+[doi.org/10.1186/s13104-022-05944-1](https://doi.org/10.1186/s13104-022-05944-1)
+
+<aside>
+<div data-badge-type="donut" data-doi="10.1186/s13104-022-05944-1" data-hide-no-mentions="true" class="altmetric-embed"></div>
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
+
+**Parsons, S.**, Azevedo, F., Elsherif, M.
+M.
+M., Guay, S., ...
+& Aczel, B.
+(2022) A Community-Sourced Glossary of Open Scholarship Terms.
+*Nature Human Behavior*.
+[doi.org/10.1038/s41562-021-01269-4](https://doi.org/10.1038/s41562-021-01269-4).
+preprint: [osf.io/preprints/metaarxiv/kdqcw](https://osf.io/preprints/metaarxiv/kdqcw).
+Open access link: [rdcu.be/cHsqM](rdcu.be/cHsqM).
+website: [forrt.org/glossary/](https://forrt.org/glossary/)
+
+<aside>
+<div data-badge-type="donut" data-doi="10.1038/s41562-021-01269-4" data-hide-no-mentions="true" class="altmetric-embed"></div>
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
+
+**Parsons, S.**, Todorovic, A., Lim, M., Songco, A., & Fox, E.
+(2022).
+Data and protocol for the Oxford Achieving Resilience during COVID-19 (ARC) study.
+*accepted for publication in the Journal of Open Psychology Data*
+
+**Parsons, S** (2020).
+Exploring reliability heterogeneity with multiverse analyses: Data processing decisions unpredictably influence measurement reliability.
+*accepted for publication at Meta-Psychology*.
+Preprint: [psyarxiv.com/y6tcz](https:/psyarxiv.com/y6tcz), data and code: [osf.io/haz6u/](https://osf.io/haz6u/)
 
@@
 
+Pownall, M., Azevedo, F., Aldoh, A., Elsherif, M.
+Vasilev, M., Pennington, C., Robertson, O., Vel Tromp, M., Lui, M., Makel, M., Tonge, N., Moreau, D., Horry, R., Shaw, J., Tzavella, L., McGarrigle, R., Talbot, C., **Parsons, S.*, & FORRT (2021).
+Embedding open and reproducible science into teaching: A bank of lesson plans and resources.
+*Scholarship of Teaching and Learning in Psychology*.
+[doi.org/10.1037/stl0000307](https://doi.org/10.1037/stl0000307)
+
+<aside>
+<div data-badge-type="donut" data-doi="10.1037/stl0000307" data-hide-no-mentions="true" class="altmetric-embed"></div>
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
+
 Lim, M.
-C., **Parsons, S.**, Goglio, A., Fox, E.
+C., **Parsons, S.**, Goglio, A., & Fox, E.
 (2021).
@@
 
-**Parsons, S** (2020).
-Exploring reliability heterogeneity with multiverse analyses: Data processing decisions unpredictably influence measurement reliability.
-Under review at Meta-Psychology.
-Preprint: [psyarxiv.com/y6tcz](https:/psyarxiv.com/y6tcz), data and code: [osf.io/haz6u/](https://osf.io/haz6u/)
-
 FORRT. (2019). Introducing a Framework for Open and Reproducible Research Training (FORRT). (Co-author). Preprint: [osf.io/bnh7p/](https://osf.io/bnh7p/). Website: [forrt.org](https://forrt.org)

### 2022-05-11 papers.Rmd
adding papers and updating cv

@@
 
-(please note: I will add pdfs links asap)
+(pdfs of all papers can be downloaded from here)
 
@@
 *BMC Research Notes, 15*, 75.
-[doi.org/10.1186/s13104-022-05944-1](https://doi.org/10.1186/s13104-022-05944-1)
+[doi.org/10.1186/s13104-022-05944-1](https://doi.org/10.1186/s13104-022-05944-1)   [<i class="fas fa-download"></i> PDF](papers/23_Azevedo_etal_2022_BMCResearchNotes.pdf)
 
@@
 Open access link: [rdcu.be/cHsqM](rdcu.be/cHsqM).
-website: [forrt.org/glossary/](https://forrt.org/glossary/)
+website: [forrt.org/glossary/](https://forrt.org/glossary/)   [<i class="fas fa-download"></i> PDF](papers/22_Parsons_etal_2022_NatureHumanBehaviour.pdf)
 
@@
 Data and protocol for the Oxford Achieving Resilience during COVID-19 (ARC) study.
-*accepted for publication in the Journal of Open Psychology Data*
+*Journal of Open Psychology Data  10(1)*, 4.
+[doi.org/10.5334/jopd.56](http://doi.org/10.5334/jopd.56)   [<i class="fas fa-download"></i> PDF](papers/21_Parsons_etal_2022_JournalofOpenPsychologyData.pdf)
+
+<aside>
+<div data-badge-type="donut" data-doi="10.5334/jopd.56" data-hide-no-mentions="true" class="altmetric-embed"></div>
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
 
@@
 *accepted for publication at Meta-Psychology*.
-Preprint: [psyarxiv.com/y6tcz](https:/psyarxiv.com/y6tcz), data and code: [osf.io/haz6u/](https://osf.io/haz6u/)
+Preprint: [psyarxiv.com/y6tcz](https:/psyarxiv.com/y6tcz), data and code: [osf.io/haz6u/](https://osf.io/haz6u/)   [<i class="fas fa-download"></i> PDF](papers/20_Parsons_2022_MetaPsychology_acceptedpreprint.pdf)
+
+<aside>
+<div data-badge-type="donut" data-doi="10.31234/osf.io/y6tcz" data-hide-no-mentions="true" class="altmetric-embed"></div>
+<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
+</aside>
 
@@
 *Scholarship of Teaching and Learning in Psychology*.
-[doi.org/10.1037/stl0000307](https://doi.org/10.1037/stl0000307)
+[doi.org/10.1037/stl0000307](https://doi.org/10.1037/stl0000307)   [<i class="fas fa-download"></i> PDF](papers/19_Pownall_etal_2021_ScholarshipofTeachingandLearninginPsychology.pdf)
 
@@
 *Journal of Eating Disorders, 9*.
-[doi.org/10.1186/s40337-021-00444-2](https://doi.org/10.1186/s40337-021-00444-2)
+[doi.org/10.1186/s40337-021-00444-2](https://doi.org/10.1186/s40337-021-00444-2)    [<i class="fas fa-download"></i> PDF](papers/18_Lim_Parsons_Goglio_Fox_2021_JournalofEatingDisorders.pdf)
 
@@
 
-**Parsons, S.**, (2021). splithalf: robust estimates of split half reliability. *Journal of Open Source Software, 6*(60), 3041, [doi.org/10.21105/joss.03041](https://doi.org/10.21105/joss.03041)
+**Parsons, S.**, (2021).
+splithalf: robust estimates of split half reliability.
+*Journal of Open Source Software, 6*(60), 3041, [doi.org/10.21105/joss.03041](https://doi.org/10.21105/joss.03041)   [<i class="fas fa-download"></i> PDF](papers/17_Parsons_2021_JournalofOpenSourceSoftware.pdf)
 
@@
 *Cognition and Emotion* \\ [doi.org/10.1080/02699931.2021.1915752](https://doi.org/10.1080/02699931.2021.1915752).
-Preprint: [psyarxiv.com/8ygn](https://psyarxiv.com/8ygnh), data and code: [osf.io/mn5ek/](https://osf.io/mn5ek/)
+Preprint: [psyarxiv.com/8ygn](https://psyarxiv.com/8ygnh), data and code: [osf.io/mn5ek/](https://osf.io/mn5ek/)    [<i class="fas fa-download"></i> PDF](papers/16_Parsons_etal_2021_CognitionandEmotion.pdf)
 
@@
 Looking back to move forward: Reflections on the strengths and challenges of the COVID-19 UK mental health research response.
-*Frontiers Psychiatry*. [10.3389/fpsyt.2021.622562](https://doi.org/10.3389/fpsyt.2021.622562)
+*Frontiers Psychiatry*. [10.3389/fpsyt.2021.622562](https://doi.org/10.3389/fpsyt.2021.622562)   [<i class="fas fa-download"></i> PDF](papers/15_Demkowicz_etal_2021_FrontiersPsychiatry.pdf)
 
@@
 Anxiety and depressive symptom trajectories in adolescence and the co-occurring development of cognitive biases: Evidence from the CogBIAS longitudinal study.
-*Journal of Abnormal Child Psychology, 48*, 1617–1633, DOI: [10.1007/s10802-020-00694-9](https://doi.org/10.1007/s10802-020-00694-9)
+*Journal of Abnormal Child Psychology, 48*, 1617–1633, DOI: [10.1007/s10802-020-00694-9](https://doi.org/10.1007/s10802-020-00694-9)    [<i class="fas fa-download"></i> PDF](papers/14_Songco_etal_2020_JournalofAbnormalChildPsychology.pdf)
 
@@
 *Development and Psychopathology*, 1-9.
-DOI: [10.1017/S0954579420000668](https://doi.org/10.1017/S0954579420000668)
+DOI: [10.1017/S0954579420000668](https://doi.org/10.1017/S0954579420000668)   [<i class="fas fa-download"></i> PDF](papers/13_Booth_etal_2020_DevelopmentandPsychopathology.pdf)
 
@@
 Trajectories of anxiety when children start school: The role of behavioral inhibition and attention bias to angry and happy faces
-*Journal of Abnormal Psychology*. DOI: [10.1037/abn0000623](https://doi.org/10.1037/abn0000623)
+*Journal of Abnormal Psychology*. DOI: [10.1037/abn0000623](https://doi.org/10.1037/abn0000623)   [<i class="fas fa-download"></i> PDF](papers/12_Dodd_etal_2020_JournalofAbnormalPsychology.pdf)
 
@@
 DOI: [10.1016/j.biopsycho.2020.107866](https://www.sciencedirect.com/science/article/pii/S0301051120300260).
-Preprint: [psyarxiv.com/4ze6h](https://psyarxiv.com/4ze6h/)
+Preprint: [psyarxiv.com/4ze6h](https://psyarxiv.com/4ze6h/)   [<i class="fas fa-download"></i> PDF](papers/11_Parsons_2020_BiologicalPsychiatry.pdf)
 
@@
 *Applied Cognitive Psychology, 34*(2).
-DOI: [10.1002/acp.3628](https://onlinelibrary.wiley.com/doi/abs/10.1002/acp.3628)[10.1002/acp.3628]
+DOI: [10.1002/acp.3628](https://onlinelibrary.wiley.com/doi/abs/10.1002/acp.3628)   [<i class="fas fa-download"></i> PDF](papers/10_Herbert_etal_2019_AppliedCognitivePsychology.pdf)
 
@@
 DOI: [doi.org/10.1177/2515245919879695](https://doi.org/10.1177/2515245919879695).
-Preprint: [psyarxiv.com/6ka9z](https://psyarxiv.com/6ka9z)
+Preprint: [psyarxiv.com/6ka9z](https://psyarxiv.com/6ka9z)   [<i class="fas fa-download"></i> PDF](papers/9_Parsons_Kruijt_Fox_2019_AMPPS.pdf)
 
@@
 *BMC Psychology, 7*, 73.
-DOI: [10.1186/s40359-019-0342-8](https://bmcpsychology.biomedcentral.com/articles/10.1186/s40359-019-0342-8)
+DOI: [10.1186/s40359-019-0342-8](https://bmcpsychology.biomedcentral.com/articles/10.1186/s40359-019-0342-8)   [<i class="fas fa-download"></i> PDF](papers/8_Booth_etal_2019_BMCPsychology.pdf)
 
@@
 DOI: [doi.org/10.1027/2151-2604/a000387](https://doi.org/10.1027/2151-2604/a000387).
-Preprint: [psyarxiv.com/cfzyx](https://psyarxiv.com/cfzyx)
+Preprint: [psyarxiv.com/cfzyx](https://psyarxiv.com/cfzyx)   [<i class="fas fa-download"></i> PDF](papers/7_Cruwell_etal_2019_ZeitschriftfürPsychologie.pdf)
 
@@
 DOI: 10.1037/abn0000406.
-Preprint DOI: [10.31234/osf.io/rfjup](10.31234/osf.io/rfjup)
+Preprint DOI: [10.31234/osf.io/rfjup](10.31234/osf.io/rfjup)   [<i class="fas fa-download"></i> PDF](papers/6_Kruijt_Parsons_Fox_2019_JournalAbnormalPsychology.pdf)
 
@@
 *Published as an eLetter on* [10.1192/bjp.2018.43](https://doi.org/10.1192/bjp.2018.43).
-Preprint: [psyarxiv.com/k3vxc](https://psyarxiv.com/k3vxc)
+Preprint: [psyarxiv.com/k3vxc](https://psyarxiv.com/k3vxc)   [<i class="fas fa-download"></i> PDF](papers/5_Parsons_2018_BritishJournalPsychiatryeLetter.pdf)
 
@@
 *Psychological Research*.
-DOI: [doi.org/10.1007/s00426-018-1081-9](https://doi.org/10.1007/s00426-018-1081-9)
+DOI: [doi.org/10.1007/s00426-018-1081-9](https://doi.org/10.1007/s00426-018-1081-9)   [<i class="fas fa-download"></i> PDF](papers/4_Notebaert_etal_2018_PsychologicalResearch.pdf)
 
@@
 DOI: [10.1038/s41562-018-0311-x](https://www.nature.com/articles/s41562-018-0311-x).
-Preprint: [psyarxiv.com/9s3y6/](https://psyarxiv.com/9s3y6/)
+Preprint: [psyarxiv.com/9s3y6/](https://psyarxiv.com/9s3y6/)   [<i class="fas fa-download"></i> PDF](papers/3_Lakens_etal_2017_NatureHumanBehavior.pdf)
 
@@
 *BMC Psychology, 5*(1).
-DOI: [doi.org/10.1186/s40359-017-0210-3](https://doi.org/10.1186/s40359-017-0210-3)
+DOI: [doi.org/10.1186/s40359-017-0210-3](https://doi.org/10.1186/s40359-017-0210-3)   [<i class="fas fa-download"></i> PDF](papers/2_Booth_etal_2017_BMCPsychology.pdf)
 
@@
 
-**Parsons, S**, Kruijt, A-W., & Fox, E. (2016). A cognitive model of psychological resilience. *Journal of Experimental Psychopathology, 7*(3), 296-310. DOI: http://dx.doi.org/10.5127/jep.053415
+**Parsons, S**, Kruijt, A-W., & Fox, E.
+(2016).
+A cognitive model of psychological resilience.
+*Journal of Experimental Psychopathology, 7*(3), 296-310.
+DOI: [10.5127/jep.053415](http://dx.doi.org/10.5127/jep.053415)   [<i class="fas fa-download"></i> PDF](papers/1_Parsons_Kruijt_Fox_2016_JournalExperimentalPsychopathology.pdf)
 

### 2022-09-07 _posts/2022-09-07-nhb-glossary/nhb-glossary.Rmd
new blog

---
title: "Responding to some critisms of the FORRT Glossary paper"
description: |
  Some people have complained that the FORRT Glossary project is paywalled. This isn't correct, and I have thoughts about concerns raised about publishing (a description of this project) in Nature Human Behaviour. Reader discression: Jaded postdoc writing becomes clearer throughout.
date: 09-07-2022
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

(These thoughts are mine and may not reflect my co-authors)

## Quick background:

For those unfamiliar, FORRT's Glossary project (<https://forrt.org/glossary/>) is a large collection of terms broadly relating to open scholarship. We hope this resource makes conversations about open scholarship more accessible, and acts as a useful resource for students and educators. Over 100 scholars contributed to the project; writing and editing descriptions, and generating a consensus for over 250 terms relating to open scholarship.

In February 2022 we published a paper describing the project in Nature Human Behaviour (publishers link to accessible version: <https://rdcu.be/cHsqM>, and post-print: <https://doi.org/10.31222/osf.io/kdqcw>). Now, I cannot stress this enough: the paper is not the glossary. The paper describes and advertises the project, while the actual resource is completely open (and still open for contributions) on the FORRT website (<https://forrt.org/glossary/>).

Unfortunately, the "official" version of the paper - the DOI'd version - is behind a paywall (<https://www.nature.com/articles/s41562-021-01269-4>). Before you gasp and complain (as some have, but we'll get to that shortly), know that we were informed only at the last minute that the paper would not be made open access. Technically the paper is a comment, and therefore deemed ineligible per journal policies to be open access. There were long drawn out battles behind the scenes to make this open access, that in the end we lost. What we were given was a publishers access link we could openly share. Not technically open access, but at least we could share that, and the postprint.

## The complaints / concerns / gripes

Once again, someone on twitter has raised concern with the Nature Human Behavior paper  describing phase 1 of the FORRT glossary project. This post isn't necessarily a direct response to any specific message. But the latest message did prompt me to write this, particularly as it felt unnecessary to add a complaint about this project after complementing Flavio Azevedo (<https://twitter.com/Flavio_Azevedo_>) on his wonderful NASA interview (<https://science.nasa.gov/open-science/transform-to-open-science/stories/dr-flavio-azevedo>). Several co-authors and I have responded to these and other concerns about the project since it was published. I cant say for others, but I can imagine a sense of disappointment that this mass community effort can be so quickly dismissed or critiqued out of hand.

Mostly at this point I'm just bored of cycling through very similar conversations, so I'm spending my morning writing this post. Honestly, I'm not sure I'll engage in some of these complaints any more other than giving the link to this post. If I seem tired and a bit jaded, it's because I am.

OK, the complaints in a somewhat discussion format (perhaps over-emphasised).

### 1. The project looks great, but I cant believe something so useful would be paywalled.

No, it's not. The project is on the website, and you can still contribute (<https://forrt.org/glossary/>). The paper is merely a summary of phase 1 of the project, and you can still access it (publishers link to accessible version: <https://rdcu.be/cHsqM>, and post-print: <https://doi.org/10.31222/osf.io/kdqcw>). We share these accessible versions everywhere, including the website, so the official DOI link can basically be ignored in favour of these (sorry, not sorry, NHB).

### 2. But, but, the paper is paywalled!

We were told it would be open (shrug emoji). Then at the last minute, because of journal policy, it was not. More than a few people spent a lot of time trying to navigate this, but we were eventually denied. Sorry if you're still disappointed in that.

### 3. How can you say you support open scholarship if you published in a Nature journal!?

Personally, I think that the glossary is more than a net benefit to academia. I know Springer, El$evier, et al. are demon spawn sent to suck academia dry. Did we feed the beast? Maybe, but they didn't get any money from us and the accessible links are what we're sharing.

I'd rather not have to rely on journals at all, but can you genuinely say that if we had "only" preprinted this paper that anywhere as many people would have seen the glossary? Is NHB a venue that would lead to a higher readership and likely credibility for the glossary? Probably, and given the sheer amount of papers and commentaries on open scholarship in there, it seems like a good way to spread the word.

Now, if this were a solo author perspective, I would have pulled it and submitted elsewhere. Or, more likely, preprinted and procrastinated on submitting. But, this was a mass effort and I dont think subjecting everyone to an entirely different submission (and likely a major revision of the comment) would have benefited anyone - including those who may benefit from the glossary itself.

### 4. Oh, so you just want the prestigue of a Nature journal.

I want recognition for the 100+ contributors on this project. I want projects like this, that would otherwise be purely powered by volunteered labour, to be recognised. I want a way for those that contributed on this, and other FORRT projects, to get credit for doing so. Does publishing in NHB maximise that, probably. Do I hate academic "prestige" in its many unjustified, gate-keeping, and inequitable awfulness. Yes. Do I recognise that publications, and especially publications in outlets like this can make a world of difference for a grass-roots, largely ECR led initiative. Also yes. Does it somehow minimise the integrity of our contributors/coauthors or the glossary project, I argue no.

### 5. Oh, so you support the current system of (exploitative) academic publishing?

Do I want the entire system to change. Yes. I'd happily see journals as we currently see them die off and replaced entirely with something better and more equitable. Was a comment paper about our glossary project the vehicle for systemic change, no.

I'm fond of the buffet table approach to open scholarship (shout out to Kirstie Whitaker <https://twitter.com/kirstie_j> for introducing many people to this idea). We can do great work and make impactful contributions in some aspects of open scholarship, but does every project have to live by the "ideal" principles of open scholarship (if folk can even agree on what those would be)? There will always be trade offs, in this instance we wanted to maximise the credit and impact of the glossary project as well as maximise the recognition for our contributors.

### 6. The paper being paywalled at NHB makes me doubt your open science awareness.

Cool, you do you. Check out the above responses. Maybe check out the glossary itself too before bashing the contributors and their expertise? Otherwise I can easily say who looks the bigger jerk in this exchange?

### 7. Your definition of [insert term] sucks!

The project is open. Add improvements, suggest alternatives. That's how it will improve.

### 8. You didn't define XYZ! (likely my special sub-domain)

Cool, see the above, you can add it yourself. We welcome contributors and their contributions.

### 9. Just like many open science movements, the project's authors are dominated by WEIRD (Western, Educated, Industrialized, Rich and Democratic societies).

I don't have the numbers on this. We did open the project and advertise widely. We are looking to begin translation projects to increase the diversity, representation, and accessibility. It wont solve this problem, but hopefully helps improve things.

### 10. General negative half-baked thoughts

Stop, do better.

## End

Thank you to everyone that contributed, and continues to contribute, to the glossary project. It's am awesome resource, and it will continue to improve. Y'all are amazing and you created something useful.

To those flinging critiques - I agree with some of your concerns, I'd prefer academia to simply be different too. I hope this post helps explain some background and my own thoughts on these critiques. I can say that my own perspectives should not be interpreted as reflecting the view of every contributor/coauthor. Still, there is a difference between critiquing this work such that improvements can be made, and mindless poo flinging.

### 2023-02-15 papers.Rmd
updated cv and pubs

@@
 
-**Parsons, S** (2020).
+**Parsons, S** (2022).
 Exploring reliability heterogeneity with multiverse analyses: Data processing decisions unpredictably influence measurement reliability.
 *accepted for publication at Meta-Psychology*.
-Preprint: [psyarxiv.com/y6tcz](https:/psyarxiv.com/y6tcz), data and code: [osf.io/haz6u/](https://osf.io/haz6u/)   [<i class="fas fa-download"></i> PDF](papers/20_Parsons_2022_MetaPsychology_acceptedpreprint.pdf)
+DOI: [doi.org/10.15626/MP.2020.2577](https://doi.org/10.15626/MP.2020.2577), data and code: [osf.io/haz6u/](https://osf.io/haz6u/)   [<i class="fas fa-download"></i> PDF](papers/20_Parsons_2022_MetaPsychology_acceptedpreprint.pdf)
 
@@
 
+**Parsons, S.**, Brandmaier, A., Lindenberger, U., & Kievit.
+(2023).
+Longitudinal stability of grey matter measures varies across brain regions, imaging metrics, and testing sites in the ABCD study.
+Preprint: https://psyarxiv.com/zpu6t/
+
+Zavlis, O., **Parsons, S.**, Fox, E., Booth, C., Songco, S., & Vincent, J.
+(December, 2022).
+The effects of life experiences and polygenic risk for depression on the development of positive and negative cognitive biases across adolescence: The CogBIAS hypothesis.
+Preprint: https://psyarxiv.com/wsn4x/
+
+**Parsons, S.** & McCormick, E.
+M.
+(November, 2022).
+“Don’t peek at your data” applies to longitudinal studies too: two time points poorly capture trajectories of change.
+Preprint: https://psyarxiv.com/
+
+Todorovic, A., *Parsons, S.*, Chapple, L., Taylor, A., & Fox, E.
+(2022, April 29).
+Lower, not higher, trait anxiety leads to switch cost asymmetry on neutral tasks: a replication and extension of Gustavson et al., 2017.
+https://doi.org/10.31234/osf.io/aer8b
+
 FORRT. (2019). Introducing a Framework for Open and Reproducible Research Training (FORRT). (Co-author). Preprint: [osf.io/bnh7p/](https://osf.io/bnh7p/). Website: [forrt.org](https://forrt.org)
